Conditions for $d$-local-connectedness of boundaries of hyperbolic groups

### 2020-02-14 paper.tex
Proof reading of sections 3-4

\begin{proposition}\label{prop:i_in_dimension_1}
  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exist $L$ and
  $n_0$ such that for $n\geq n_0$ there is a map $i^n_{n+1}\from \Skel_1 K_n
  \to \Skel_1 K_{n+1}$ satisfying the following conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
    \item for each $n$, the map $i^n_{n+1}$ is affine homotopic to a map that
      factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

@@

We now introduce a new condition, which should be thought of as a version of
$\ddag_M$ one dimension higher.

@@

\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
  If $G$ satisfies $\S_M$ for all $M$ then $\boundary G$ is locally simply
  connected.
\end{restatable}

Thrououghout the rest of this section we assume that $G$ satisfies
\todo{conditions.}

@@

\begin{proof}
  \todo{Prove this}
\end{proof}

@@

\begin{lemma}\label{lem:useful}
  \todo{Or quasi-geodesics?}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then,
  \begin{equation*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{equation*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

\begin{proof}
  We estimate the Gromov product using the visual metric $\vdistance$ on 
  $\boundary G$; then the claimed inequality follows from the triangle 
  inequality.

  Let $i_n = \dist(x_n, e)$, so $i_n = i_0 + n$, and let 
  $\dist(x_{n+1},x_n)$ be bounded by $C_0$. By 
  \cref{lem:near_geod_rays} there exists a sequence $(\alpha_n)$ of 
  geodesic rays with $\dist(\alpha_n(i_n), x_n) \leq 4\delta$. Then 
  $\dist(\alpha_n(i_n), \alpha_{n+1}(i_{n+1})) \leq C_0 + 8\delta$. Then 
  $\gromov{e}{\alpha_n(\infty)}{ \alpha_{n+1}(\infty)} \geq i_n - (C_0 + 
  8\delta)/2$.

  By the triangle inequality it follows that for $n\geq m$ we have the following 
  inequality.
  \begin{equation*}
    \vdistance(\alpha_n(\infty), \alpha_m(\infty)) \leq C_1 a^{-i_m}
  \end{equation*}
  for some constants $C_1$ depending only on $\delta$ and $C_0$. Then, by
  definition of the visual metric, there exists a constant $C_2$ such that
  \begin{equation*}
    \gromov{e}{\alpha_n(\infty)}{\alpha_m(\infty)} \geq i_m - C_2.
  \end{equation*}
  Now, by \cref{lem:boundary_gromov_product} there exists a constant $C_3$ such
  that
  \begin{equation*}
    \gromov{e}{\alpha_n(i_n)}{\alpha_m(i_m)} \geq i_m - C_3,
  \end{equation*}
  as required.
\end{proof}

@@

\begin{proof}
  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
  = \dist(e, y_n)$.

  We now bound the distance $\dist(y_n, y_{n+1})$. To start with, $\dist(y_n,
  i^n_{n+1} y_n) \leq 2\delta+1$. Let $R$ be $3\cdot 2^{k-1}$, so that any two
  vertices in the 1-skeleton of $\sd^k \Delta$ are joined by a path
  traversing at most $R$ edges. Let $\sigma$ be the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$ and $y_{n+1}$ is a
  vertex of the image of $\sigma$ under $i^n_{n+1}$, so $\dist(i^n_{n+1} y_n,
  y_{n+1}) \leq RD$.  Putting this together,
  \begin{equation*}
    \dist(y_n, y_{n+1}) \leq (2\delta + 1) + RD
  \end{equation*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.

  Finally, by applying the inequality in \cref{rem:dist_vs_newdist}, we deduce
  that
  \begin{equation*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{equation*}
\end{proof}

@@

\begin{proof}
  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
  tends to infinity as $n_1$ and $n_2$ tend to infinity.
\end{proof}

@@

\begin{proof}
  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
  and $y$. By~\cite[Proposition III.H.1.22]{bridsonhaefliger99} there exist
  $\delta'$ depending only on $\delta$ such that
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
    &\geq \min\{m - C, m - R/2, m - C\} - 2\delta' \\
    &\geq m - C'
  \end{align*}
  for some constant $C'$.
\end{proof}

@@

\begin{corollary}\label{cor:visualdiameter}
  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
  $\sigma$ of $\Skel_2 K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$,
  where $a$ is the visual parameter.\qed
\end{corollary}

@@

\begin{remark}
  In fact, if $K_m$ is endowed with a metric in which each simplex is 
  isometrically identified with the standard simplex of the same dimension then 
  the map $i^m_\infty$ can be shown to be H\"{o}lder continuous with exponent 
  only depending on $\delta$ and $k$.  We do not require this strengthening of
  \cref{prop:continuouslimit} here.
\end{remark}

Finally, we use the maps $i^n_\infty$ to construct homotopies between certain
special maps to $\boundary G$.

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a constant. Then there exist numbers $m_0$ and $\mu$
  with the following property. Let $n \geq m_0$ and let $\gamma_0$ and
  $\gamma_1$ be maps from $\boundary\Delta\to\boundary G$. Let $f_0$ and $f_1$
  be simplicial approximations to $p^\infty_n\composed \gamma_0$ and
  $p^\infty_n\composed\gamma_1$. Suppose that $\newdist(f_0(x), f_1(x))\leq C$
  for every $x \in \boundary \Delta$. Then there is a homotopy $h$ from
  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a uniform
  continuity condition: for any $x \in \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\} \times [0,1])) \leq \mu a^{-n},
  \end{equation*}
  where the diameter is taken with respect to the visual metric.
\end{proposition}

\begin{proof}
  \todo{constant on ddag}
  Let $G$ satisfy $\ddag'_?$ with constants $L$ and $m_0 \geq n_0$.
  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then we have a map 
  \begin{equation*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{equation*}
  defined on a subset of the product simplicial complex $J \times [0,1]$ and
  this map is a simplicial approximation to the map $\gamma_0 \disjointunion
  \gamma_1$ from $J\times\{0\} \disjointunion \{1\}$ to $\boundary G$.

  Using $\ddag'_?$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
  along each edge $x\times [0,1]$, when composed with $p^\infty_n$ admits a
  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
  that $f_0 \disjointunion f_1$ admints an extension to $J \times [0,1]$ after
  only $k'$ barycentric subdivisions. Call the extension $F$ and let $h =
  i^n_\infty \composed F$, so that $h$ is a homotopy from $i^n_\infty\composed
  f_0$ to $i^n_\infty\composed f_1$. It remains to prove the bounded distance
  assertion.

  Let $M$ be the number of $2$-simplices in $\sd^{k'}([0,1]^2)$.
  Corollary~\ref{cor:visualdiameter} gives a constant $C_0$ so that any
  $2$-simplex is mapped by $i^n_\infty$ to a set of diameter at most $C_0
  a^{-n}$, and so we can take $\mu = MC_0$.
\end{proof}

\subsection{Proving \Cref{thm:ddagimpliesLCd}}

We now use the maps $(i^n_{n+1})$ to prove \cref{thm:ddagimpliesLCd}. We begin
with two lemmas.

\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that the distance from $(i^m_\infty \composed 
  p^\infty_m)$ to the identity map $\boundary G\to\boundary G$ is at most 
  $Ca^{-m}$ for each $m \geq n_0$.
\end{lemma}

\begin{proof}
  Let $\xi \in \boundary G$. By \cref{lem:linearproduct} there is a 
  constant $C$ such that 
  \begin{equation*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{equation*} 
  for each $n\geq m\geq n_0$.

  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
  that
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
            - 2\delta' \\
          &\geq \min\{m - C, m - R/2, m\} - 2\delta' \\
          &\geq m - C'
  \end{align*}
  for some constant $C'$.

@@

\begin{proof}
  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
  of a simplex containing $p^\infty_n(\xi)$; then $\newdist(y, p^\infty_n(\xi))$
  is bounded by $D$.

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
  the product of $D$ and the constant $k$ appearing in
  \cref{prop:i_in_dimension_2}. By putting all this together we obtain a bound
  $C$ on $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$,
  and then $\dist(x_1, x_2) \leq C + 2D$.
\end{proof}

\begin{proposition}\label{prop:uniform_homotopies}
  There exists numbers $m_0$ and $\nu$ with the following property. Let
  $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
  m_0$ and let $f$ be an affine approximation to $p^\infty_n\composed\gamma$.
  Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
  that for any $x \in \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\}\times [0,1])) \leq \nu a^{-n}.
  \end{equation*}
\end{proposition}

@@

  \todo{Justify the application of the proposition.}

@@

  Let $x \in \boundary\Delta$ and let $\epsilon > 0$. There exists $M$ such
  that for $m \geq M$ and $y \in \boundary \Delta$, $\rho(\gamma(y),
  \gamma_m(y)) \leq \epsilon/3$. Increasing $M$ if necessary we may assume that
  \begin{align*}
    \sum_m \geq M \mu a^{-m-n} \leq \epsilon/3.
  \end{align*}
  Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}$,
  \begin{equation*}
    \rho{h(x,0), h(y,t)} \leq \frac{\epsilon}{3} + \frac{\epsilon}{3} +
        \frac{\epsilon}{3} = \epsilon.
  \end{equation*}
  Therefore $h$ is continuous.

  Finally, we immediately see that for any $x \in \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\}\times (0,1])) \leq \mu \left(\sum_{m\geq 0} a^{-m}\right)a^{-n},
  \end{equation*}
  and then $\Diam(h(\{x\}\times [0,1]))$ satisfies the same inequality by
  continuity of $h$.
\end{proof}

\Cref{thm:ddagimpliesLCd} follows as a corollary of this proposition.

@@

  Let $\gamma\from\boundary\Delta\to\boundary G$ be such a map. Let 
  \begin{equation*}
    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0,
  \end{equation*}
  so that by \cref{lem:projectstoasimplex} $p^\infty_{m}\composed\gamma$ has
  image contained in a single vertex of $K_m$. Then a constant map
  $\boundary\Delta \to K_m$ is a simplicial approximation to
  $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
  this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.

@@

\section{Simply connected point complements}

@@

\begin{proof}
  Suppose that the condition is not satisfied. Then for each $i$ there exists a
  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
  and a simplicial map $f_i \from \sd^M \boundary\Delta \to K_{n_i}$ that is a
  simplicial approimxation to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$
  does not admit an extension to $\Delta$ that is affine on $\sd^i\Delta$.

  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
  nullhomotopic by a simplicial map, and this gives a contradiction for $i$
  sufficiently large.

  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
  image of $\gamma_i$ for every $i \geq i_0$. By
  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
  $q_i\restricted{C_0}$ is affine homotopic to $q_{i_1}\restricted{C_0}$ for
  every $i \geq i_1$.

  Let $h$ be a nullhomotopy of $\gamma_{i_1}$ in
  $\boundary G - \set\xi$ and let $C_1$ be a compact subset of $\boundary G -
  \set\xi$ containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1
  \subset U_{i_2}$.

  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
  to a point.
  \todo{would just $i_0$ and $i_1$ have been enough?}
\end{proof}

>>>>

\begin{proposition}\label{prop:i_in_dimension_1}
  Suppose that $G$ satisfies $\ddag'_{D + 4\delta+2}$. Then there exist $L$ and
  $n_0$ such that for $n\geq n_0$ there is a map $i^n_{n+1}\from \Skel_1 K_n
  \to \Skel_1 K_{n+1}$ satisfying the following conditions:
  \begin{enumerate}
    \item for each $n$, $i^n_{n+1}$ is an affine map on the subdivision
      $\sd_L\Skel_1 K_n$,
    \item for any vertex $x$ of $K_n$, $\dist(x, i^n_{n+1}(x)) \leq 2\delta+1$,
      and
    \item for each $n$, the map $i^n_{n+1}$ is a simplicial approximation a map
      that factors through $p^\infty_{n+1}\from \boundary G \to K_{n+1}$.
  \end{enumerate}
\end{proposition}

@@

We now introduce a new condition, which should be thought of as a version of
$\ddag_M$ describing connectedness one dimension higher.

@@

\begin{restatable}{theorem}{ddagimpliesLCd}\label{thm:ddagimpliesLCd}
  If $G$ satisfies $\ddag'_M$ and $\S_M$ for all $M$ then $\boundary G$ is
  locally simply connected.
\end{restatable}

Thrououghout the rest of this section we assume that $G$ satisfies
$\ddag'_M$ and $\S_M$ for all $M$.

@@

\begin{proof} 
  Let $n_0$ be as in Proposition~\ref{prop:i_in_dimension_1} and for $n \geq
  n_0$ let $i^n_{n+1} \from \Skel_1 K_n \to \Skel_1 K_{n+1}$ be the maps given
  by that proposition, so there exists $M$ such that $i^n_{n+1}$ is a
  simplicial map on $\sd^M\Skel_1 K_n$, and this map is a simplicial
  approximation to a map that factors through $p^\infty_{n+1} \from \boundary G
  \to K_{n+1}$.

  Then $\S_M$ gives numbers $L$ and $n_0' \geq n_0$ such that for $n \geq
  n_0'$, for any 2-simplex $\sigma$ of $K_n$, $i^n_{n+1}\restricted\boundary
  \sigma$ admits an extension to $\sigma$ that is affine on $\sd^L\sigma$.
  Gluing these extensions together extends $i^n_{n+1}$ to a map $\sd^2 K_n \to
  \sd_2 K_{n+1}$ with the required properties.
\end{proof}

@@

\begin{lemma}\label{lem:useful}
  Let $(x_n)$ be a sequence of points in $G$ with $\dist(x_{n+1}, e) = 
  \dist(x_n, e) + 1$ and $\dist(x_{n+1}, x_n)$ bounded. Then for $n \geq m$,
  \begin{equation*}
    \gromov{e}{x_m}{x_n} \geq \dist(e,x_m) - C
  \end{equation*}
  for some constant $C$ depending only on $\delta$ and the bound on 
  $\dist(x_{n+1}, x_n)$.
\end{lemma}

\begin{proof}
  By the triangle inequality, for any $n$ and $m$ we have $\dist(x_n, x_m) \geq
  \abs{n - m}$.  On the other hand, let $B$ be the bound on $\dist(x_{n+1},
  x_n)$. Then for any $n$ and $m$ we have $\dist(x_n, x_m) \leq B\abs{n - m}$. 
  Finally, $\dist(e, x_n) = \dist(e, x_0) + n$.

  It follows that the concatenation of a geodesic $[e, x_0]$ with the sequence
  $(x_n)_{n = 0}^\infty$ is a quasi-geodesic with constants depending only on
  $B$. Therefore by~\cite[Theorem III.H.1.7]{bridsonhaefliger99} there is a
  number $R$ depending only on $B$ and $\delta$ such that the sequence $(x_n)$
  is contained in an $R$-neighbourhood of a ray starting at $e$; let $(y_n)$ be
  a sequence of points on this geodesic with $\dist(y_n, x_n) \leq R$. Then
  $\gromov{e}{y_m}{y_n} = \min\{\dist(e, y_m), \dist(e, y_n)\}$, and the result
  follows with $C = 5R/2$.
\end{proof}

@@

\begin{proof}
  For $n \geq m$, let $y_n$ be a vertex of the minimal simplex of $K_n$
  containing $i^m_n(x)$. Then, for each $n \geq m$, we have $\dist(e, y_{n+1})
  = \dist(e, y_n)$.  We now bound the distance $\dist(y_n, y_{n+1})$. To start
  with, $\dist(y_n, i^n_{n+1} (y_n)) \leq 2\delta+1$. Let $R$ be $3\cdot
  2^{k-1}$, so that any two vertices in the 1-skeleton of $\sd^k \Delta$ are
  joined by a path traversing at most $R$ edges. Let $\sigma$ be the minimal
  simplex of $K_n$ containing $i^m_n(x)$. Then $y_n$ is a vertex of $\sigma$
  and $y_{n+1}$ is a vertex of the image of $\sigma$ under $i^n_{n+1}$, so
  $\dist(i^n_{n+1} y_n, y_{n+1}) \leq RD$.  Putting this together,
  \begin{equation*}
    \dist(y_n, y_{n+1}) \leq (2\delta + 1) + RD
  \end{equation*}

  It follows from \cref{lem:useful} that there exists a constant $C$ depending
  only on $\delta$ and $k$ such that $\gromov{e}{y_n}{y_m} \geq m -
  C$.  By applying the inequality in \cref{rem:dist_vs_newdist}, we deduce that
  \begin{equation*}
      \gromov{e}{i^m_n(x)}{x} \geq m - C - 3D.\qedhere
  \end{equation*}
\end{proof}

@@

\begin{proof}
  For $n_1$ and $n_2$ at least $m$, \cref{lem:linearproduct} implies that
  $\gromov{e}{i^m_{n_1}(x)}{i^m_{n_2}(x)} \geq \min\{n_1,n_2\} - C$, which
  tends to infinity as $n_1$ and $n_2$ tend to infinity. Therefore
  $(i^m_n(x))_{n=m}^\infty$ converges to a point in $\boundary G$,
  by~\cite[Lemma III.H.3.13]{bridsonhaefliger99}.
\end{proof}

@@

\begin{proof}
  The inequality of \cref{lem:linearproduct} is satisfied for each of $x$ 
  and $y$. By~\cite[Proposition III.H.1.22]{bridsonhaefliger99} there exist
  $\delta'$ depending only on $\delta$ such that
  \begin{align*}
    \gromov{e}{i^m_n(x)}{i^m_n(y)} &\geq \min\{\gromov{e}{i^m_n(x)}{x}, 
    \gromov{e}{x}{y}, \gromov{e}{y}{i^m_n(y)}\} - 2\delta'\\
    &\geq \min\{m - C, m - D/2, m - C\} - 2\delta' \\
    &\geq m - C'
  \end{align*}
  for some constant $C'$.
\end{proof}

@@

\begin{corollary}\label{cor:visualdiameter}
  There is a constant $C$ such that for any $m\geq n_0$ and any simplex
  $\sigma$ of $\Skel_2 K_m$, the diameter of $i^m_{\infty}(\sigma)$ with
  respect to the visual metric $\vdistance$ is bounded above by $Ca^{-m}$.
\end{corollary}

@@

\begin{remark}
  In fact, if a 2-simplex of $K_m$ is metrically identified with the standard
  2-simplex then the restriction of $i^m_\infty$ to this simplex can be shown
  to be H\"{o}lder continuous.  We do not require this strengthening of
  \cref{prop:continuouslimit} here.
\end{remark}

\subsection{Homotopies in $\boundary G$}

We now use the maps $i^n_\infty$ to construct homotopies in $\boudndary G$. To
begin, we prove the following proposition, which constructs homotopies between
certain special maps.

\begin{proposition}\label{prop:basic_homotopies}
  Let $C$ be a positive number. Then there exist numbers $m_0$ and $\mu$
  with the following property. Let $n \geq m_0$ and let $\gamma_0$ and
  $\gamma_1$ be maps from $\boundary\Delta\to\boundary G$. Let $f_0$ and $f_1$
  be simplicial approximations to $p^\infty_n\composed \gamma_0$ and
  $p^\infty_n\composed\gamma_1$. Suppose that $\newdist(f_0(x), f_1(x))\leq C$
  for every $x \in \boundary \Delta$. Then there is a homotopy $h$ from
  $i^n_\infty\composed f_0$ to $i^n_\infty\composed f_1$ satisfying a bounded
  length condition: for any $x \in \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\} \times [0,1])) \leq \mu a^{-n},
  \end{equation*}
  where the diameter is taken with respect to the visual metric.
\end{proposition}

\begin{proof}
  \todo{Think about condition for apply Sd}
  Let $G$ satisfy $\ddag'_C$ with constants $L$ and $m_0 \geq n_0$.
  By increasing $m_0$ we can also assume that $G$ satisfies $\S_?$ with
  constants $L'$ and $m_0$.

  Let $n \geq m_0$.  Let $J$ be a subdivision of $\boundary\Delta$ such
  that $f_0$ and $f_1$ are both affine on $J$. Then we have a map 
  \begin{equation*}
    f_0 \disjointunion f_1 \from J \times \{0\} \disjointunion J \times \{1\}
          \to K_n,
  \end{equation*}
  defined on a subset of the product simplicial complex $J \times [0,1]$ and
  this map is a simplicial approximation to the map $\gamma_0 \disjointunion
  \gamma_1$ from $J\times\{0\} \disjointunion J \times\{1\}$ to $\boundary G$.

  Using $\ddag'_C$ we can extend $\gamma_0\disjointunion\gamma_1$ along $x
  \times [0,1]$ for each vertex $x$ of $J$ in such a way that the extension
  along each edge $x\times [0,1]$, when composed with $p^\infty_n$, admits a
  simplicial approximation connecting $f_0(x)$ to $f_1(x)$ after at most $L$
  subdivisions of the interval. Finally, using the condition $\S_?$, we deduce
  that $f_0 \disjointunion f_1$ admints an affine extension to $\sd^{L'}(J
  \times [0,1])$ after Call the extension $F$ and let $h = i^n_\infty \composed
  F$, so that $h$ is a homotopy from $i^n_\infty\composed f_0$ to
  $i^n_\infty\composed f_1$.

  It remains to prove the bounded length assertion.  Let $M$ be the number of
  $2$-simplices in $\sd^{L'}([0,1]^2)$.  Corollary~\ref{cor:visualdiameter}
  gives a constant $C_0$ so that any $2$-simplex is mapped by $i^n_\infty$ to a
  set of diameter at most $C_0 a^{-n}$, and so we can take $\mu = MC_0$.
\end{proof}

We now need two more lemmas.

\begin{lemma}\label{lem:convergestoidentity}
  There is a constant $C$ such that the distance from $i^m_\infty \composed 
  p^\infty_m$ to the identity map $\boundary G\to\boundary G$ is at most 
  $Ca^{-m}$ for each $m \geq n_0$.
\end{lemma}

\begin{proof}
  By \cref{lem:linearproduct} there is a constant $C$ such that  for $\xi \in
  \boundary G$,
  \begin{equation*}
    \gromov{e}{i^m_n\composed p^\infty_m(\xi)}{p^\infty_m(\xi)} \geq m - C
  \end{equation*} 
  for each $n\geq m\geq n_0$.

  Let $\alpha$ be a geodesic ray with $\alpha(0) = e$ and $\alpha(\infty) = 
  \xi$. Then $\alpha(m)$ is a vertex of a simplex in $\Skel_2K_m$ containing 
  $p^\infty_m(\xi)$, and $\gromov{e}{\alpha(m)}{\alpha(n)} = m$ for $n\geq m$.
  It follows that there is a constant $\delta'$ depending only on $\delta$ such 
  that
  \begin{align*}
    \mathrlap{\gromov{e}{\alpha(n)}{i^m_n\composed p^\infty_m(\xi)}}\quad\quad &\\
          & \geq \min\{\gromov{e}{\alpha(n)}{\alpha(m)}, 
            \gromov{e}{\alpha(m)}{p^\infty_m(\xi)}, 
            \gromov{e}{p^\infty_m(\xi)}{i^m_n\composed p^\infty_m(\xi)}\} 
            - 2\delta' \\
          &\geq \min\{m, m - D/2, m - C\} - 2\delta' \\
          &\geq m - C'
  \end{align*}
  for some constant $C'$.

@@

\begin{proof}
  By \cref{lem:close_projections} the distances $\newdist(p^\infty_n(\xi),
  p^\infty_{n+1}(\xi))$ are bounded by $6\delta + 3 + 2D$. Let $y$ be a vertex
  of a minimal simplex containing $p^\infty_n(\xi)$; then $\newdist(y,
  p^\infty_n(\xi))$ is bounded by $D$.

  Furthermore, $\dist(y, i^n_{n+1}(y))$ is bounded by $2\delta+1$, and
  $\newdist(i^n_{n+1}(y), i^n_{n+1}\composed p^\infty_n (\xi))$ is bounded by
  the product of $D$ and the the number of 2-simpices in $\sd^L\Delta$, where
  $L$ is the number appearing in Proposition~\ref{prop:i_in_dimension_2}.  By
  putting all this together we obtain a bound $C$ on
  $\newdist(i^n_{n+1}\composed p^\infty_n(\xi), p^\infty_{n+1}(\xi))$, and then
  $\dist(x_1, x_2) \leq C + 2D$.
\end{proof}

\begin{proposition}\label{prop:uniform_homotopies}
  There exists numbers $m_0$ and $\nu$ with the following property. Let
  $\gamma\from\boundary\Delta\to\boundary G$ be a continuous map. Let $n \geq
  m_0$ and let $f$ a simplicial approximation to $p^\infty_n\composed\gamma$.
  Then there is a homotopy $h$ from $\gamma$ to $i^n_\infty\composed f$ such
  that for any $x \in \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\}\times [0,1])) \leq \nu a^{-n}.
  \end{equation*}
\end{proposition}

@@

  \todo{This still doesn't feel quite there yet.}
  For each $m$ we can apply Proposition~\ref{prop:basic_homotopies} to the maps
  $f_{m+1}$ and $i^{n+m}_{n+m+1}\composed f_m$: Lemma~\ref{lem:name_this} gives
  the bounded distance assumption, $f_{m+1}$ is a simplicial approximation to
  $p^\infty_{n+m+1}\composed\gamma$, and $i^{n+m}_{n+m+1}\composed f_{m+1}$ is
  also a simplicial approximation to a map that factors through
  $p^\infty_{n+m+1}$ because the restriction of $i^{n+m}_{n+m+1}$ to $\Skel_1
  K_{n+m}$ has this property.

@@

  Let $x \in \boundary\Delta$ and let $\epsilon > 0$. There exists $M$ such
  that for $m \geq M$ and $y \in \boundary \Delta$, $\rho(\gamma(y),
  \gamma_m(y)) \leq \epsilon/3$. Increasing $M$ if necessary we may assume that
  $\mu a^{-m-n} \leq \epsilon/3$.
  Finally, let $U$ be a neighbourhood of $x$ such that $\rho(\gamma(x),
  \gamma(y)) \leq \epsilon/3$ for $y \in U$. Now, for any $y \in U$ and $t \in (0, 2^{-M}]$,
  \begin{equation*}
    \rho(h(x,0), h(y,t)) \leq \frac{\epsilon}{3} + \frac{\epsilon}{3} +
        \frac{\epsilon}{3} = \epsilon.
  \end{equation*}
  Therefore $h$ is continuous.

  To prove the final claim, we immediately see that for any $x \in
  \boundary\Delta$,
  \begin{equation*}
    \Diam(h(\{x\}\times (0,1])) \leq \mu \left(\sum_{m\geq 0} a^{-m}\right)a^{-n},
  \end{equation*}
  and then $\Diam(h(\{x\}\times [0,1]))$ satisfies the same inequality by
  continuity of $h$.
\end{proof}

\Cref{thm:ddagimpliesLCd} follows from this proposition:

@@

  Let $\gamma\from\boundary\Delta\to\boundary G$ be such a map. Let 
  \begin{equation*}
    m = \floor{\log_a(k_1/\Diam\image\gamma)} \geq m_0.
  \end{equation*}
  Then a constant map $\boundary\Delta \to K_m$ is a simplicial approximation
  to $p^\infty_m\composed\gamma$; applying \cref{prop:uniform_homotopies} to
  this map immediately gives a homotopy $h$ from $\gamma$ to the constant map.

@@

\section{Simply connected point complements}
\todo{Move this section into section 3}

@@

\begin{proof}
  Suppose that the condition is not satisfied. Then for each $i$ there exists a
  number $n_i \geq i$, a map $\gamma_i \from \boundary\Delta \to \boundary G$
  and a simplicial approximation $f_i \from \sd^M \boundary\Delta \to K_{n_i}$
  to $p^\infty_{n_i}\composed\gamma_i$ such that $f_i$ does not admit an
  extension to $\Delta$ that is affine on $\sd^i\Delta$.

  Fix a vertex $v$ of $\boundary\Delta$; then there exist group elements $g_i
  \in G$ such that $g_i\cdot f_i(v)$ is a fixed vertex of $K$. Pass to a
  subsequence as in Section~\ref{sec:horoball}, and to a deeper subsequence so
  that $g_i\cdot f_i(w)$ is independent of $i$ for all vertices $w \in \sd^M
  \boundary\Delta$. Then the map $g_i\composed f_i$ is independent of $i$; call
  this map $f$. It remains to show that $f$ is nullhomotopic in $H$; then it is
  nullhomotopic by an affine map by~\cite{zeeman64}, and this gives a
  contradiction for $i$ sufficiently large.

  By Lemma~\ref{lem:propermaps} there exists $i_0$ and a 
  compact set $C_0 \subset \boundary G - \set\xi$ such that $C_0$ contains the
  image of $\gamma_i$ for every $i \geq i_0$. By
  Lemma~\ref{lem:affinehomotopic} there exists $i_1 \geq i_0$ such that
  $q_i\restricted{C_0}$ is homotopic to $q_{i_1}\restricted{C_0}$ for every $i
  \geq i_1$.

  Let $h$ be a contracting homotopy of $\gamma_{i_1}$ in $\boundary G -
  \set\xi$ and let $C_1$ be a compact subset of $\boundary G - \set\xi$
  containing $C_0$ and the image of $h$. Let $i_2$ be so that $C_1 \subset
  U_{i_2}$.

  Then $f$ is homotopic to $q_{i_1}\composed\gamma_{i_1}$, which is homotopic
  to $q_{i_2}\composed\gamma_{i_1}$, which is homotopic by $q_{i_2}\composed h$
  to a point.
\end{proof}
